article title

### 2022-07-12 article.tex
Add, revise content
Refactor to use biblatex

% set references indent

@@

\newpage
\section{Citations}
\label{sec:citations}
The formatting of the bibliography is not quite what I wish. I will explore bibtex for this. For now, here is how to site articles, books, and online references.

The definitive book on MSA is by Wheeler \cite{wheeler2006}. The definitive book on SPC is by Wheeler \cite{wheeler2004}. The original article on Taguchi indices was by Russell Boyles \cite{boyles1991}. A very good article on the $C_\text{pm}$ index is found in Chen et.al. \cite{chan1988}. Gunter \cite{gunter1989}.

@@

\newpage
\nocite{*}
\bibliographystyle{plain}
\bibliography{pilon_gilles}

>>>>

% useful for the bibliography
\usepackage[style=numeric]{biblatex}
\addbibresource{pilon_gilles.bib}

@@

\newpage
\section{Citations}
\label{sec:citations}

% The definitive book on MSA is by Wheeler \cite{wheeler2006}. The definitive book on SPC is by Wheeler \cite{wheeler2004}. The original article on Taguchi indices was by Russell Boyles \cite{boyles1991}. A very good article on the $C_\text{pm}$ index is found in Chen et.al. \cite{chan1988}. Gunter \cite{gunter1989}.

Here is a single citation. \cite{wheeler2006}

@@

\newpage
\section{References}
\nocite{*}
\printbibliography[heading=none]
\label{sec:references}
